The \project{unRAVE} catalog

### 2016-09-08 article/unrave.tex
Add text about errors

The weighted $\teff$ and $\logg$ values for stars meeting different
S/N constraints are shown in Figure \ref{fig:test-set-hrd}, both in logarithmic density
and mean metallicity.  The artefacts from individual models are no longer 
apparent, and stars across the full Hertzsprung-Russell diagram are visible.
However, there are a number of caveats introduced by the choices we have made to
combine estimates from multiple models.  We discuss these issues in detail in
Section \ref{sec:discussion}.

@@

\subsection{Multi-epoch observations}
\label{sec:repeat-observations}

@@

For every star
with multiple visits we constructed a high S/N stacked spectrum for that
star, weighted by the inverse variances in the individual visit spectra.

We treated the stacked spectra as normal survey stars.  We inferred labels
using all models and joined the results as per Section \ref{sec:joining-the-models}.  The labels inferred from the stacked spectra served as the basis
of comparison for all individual visits to that object.  Figure 
\ref{fig:formal-errors-comparison} shows the difference in labels 
between the comparison spectrum and a repeat visit, normalized by their 
formal errors summed in quadrature (e.g., 
$\Delta\logg/\sqrt{\sigma_{\logg,stacked}^2 + \sigma_{\logg,visit}^2}$).
If our measurements were unbiased by S/N and the formal errors were 
representative, these values should be normally distributed with a zero 
mean and unit variance.
\stub{Are they? (Probably not!). How much should we inflate our formal errors, and should this be as a function of S/N? Note that in all Figures and tables,
we show these inflated errors only, as we gauge them to be more representative.}

\stub{In Figure \ref{fig:repeat-visits} we look at the difference as a function of SNR}

>>>>

The weighted $\teff$ and $\logg$ values for stars meeting different S/N 
constraints are shown in Figure \ref{fig:test-set-hrd}, both in logarithmic 
density and mean metallicity.  The artefacts from individual models are no 
longer apparent, and the complete structure of the Hertzsprung-Russell diagram
is visible.  However, there are a number of caveats introduced by the choices 
we have made to combine estimates from multiple models.  We discuss these 
issues in detail in Section \ref{sec:discussion}.

@@

\subsection{Internal validation}
\subsubsection{Repeat observations}
\label{sec:repeat-observations}

@@

We calculated all possible pair-wise differences between the labels we
derived from multiple visits.  If \rave\ observed a star $H$ times, there 
are $H!/2(H-2)!$ possible $a$-$b$ pair-wise combinations where we can calculate 
the difference between the derived label (for example, $\logg$) over the
quadrature sum of their formal uncertainties,
\begin{eqnarray}
\eta_{\logg} & = & \frac{\logg_a - \logg_b}{\sqrt{\sigma_{\logg,a}^2 + \sigma_{\logg,b}^2}} \quad .
\end{eqnarray}

If our derived labels and formal errors were correct, the distribution of
$\eta$ values would represent a normal distribution with zero mean and
unity variance.  However, our formal errors are likely to be under-estimated,
and therefore we introduce a systematic error floor for each label, which
is added in quadrature to every observation such that for $\logg$,
\begin{eqnarray}
	\eta_{\logg} & = & \frac{\logg_a - \logg_b}{\sqrt{(\sigma_{\logg,a} + \sigma_{\logg,floor})^2 + (\sigma_{\logg,b} + \sigma_{\logg,floor})^2}} \quad .
\end{eqnarray}

We increased the minimum label error until the distribution of $\eta$ 
values for a given label approximately reached unity.  The minimum error
values for each label are shown with the distribution of (new) $\eta$
values in Figure \ref{fig:pairwise-metrics}.  These minimum values form
part of our error model, and \emph{have} been added in quadrature with 
the formal errors; the quoted errors in our labels already incorporate
these minimum errors.

\subsubsection{Precision as a function of S/N ratio}
\label{sec:precision-wrt-snr}

We also used the repeat observations to build intuition for the label
precision that was achievable as a function of S/N ratio.  Specifically
we stacked all spectra for a given star by summing the fluxes weighted
by the inverse variances, then treated the stacked spectra as a normal
survey star.  We inferred labels for the stacked spectra using all models,
and derived a joint estimate as per Section~\ref{sec:joining-the-models}.
The labels we inferred from the stacked spectrum serve as a basis of
comparison for the labels we derived from the individual visit spectra,
which are of lower S/N ratios.

In Figure \ref{fig:formal-errors-comparison} we show the RMS difference
in labels between the stacked spectrum and a single visit, binned by the
S/N ratio of the individual visit spectrum.  Here we only show stars
where the \emph{stacked} spectrum had S/N $>100$~pixel$^{-1}$ to ensure
that our baseline comparisons were in a region where we are dominated
by systematic uncertainties.  The precision in all labels tends to
flatten out past S/N $> 40$~pixel$^{-1}$, and the precision at high S/N
ratios is comparable to the minimum error floors we adopted in Section
\ref{fig:repeat-observations}.
